### 2011-01-31 trunk/papers/webist2011/paper_sec_wrapping.tex
rotated Figure 3 for larger size.
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@1221 d8b0c59b-6544-0410-94d9-83a5658a058e

\subsection{Constructing Service Requests} % (fold)
\label{sub:constructing_service_requests}

In this section we illustrate the interaction with RESTful services on simple GET requests\footnote{Other methods such as POST or SOAP-based services are also supported.}. 
In this case, a service request is assembled using its URL and a set of parameters. As an example, we will look at the eBay Shopping web service. 
To define the desired pre-condition and the type of post-condition of a new service wrapper, the service wrapper tool provides a form (not shown here). For the current example, we assume that the user has defined a pre-condition \emph{search\_key}.

We are invoking the service to retrieve a list of items corresponding to the search keyword ``USB'':

@@

\subsection{Interpreting Service Responses} % (fold)
\label{sub:interpreting_service_responses}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\linewidth]{images/ServiceWrapperToolGVSWithTransformationRules.png}
    \caption{Rule-based transformation of service response}
    \label{fig:response_service_execution}
  \end{center}
\end{figure}

@@

\subsection{Generating the Service Wrapper} % (fold)
\label{sub:generating_a_resource_adapter}

>>>>

%\subsection{Constructing Service Requests} % (fold)
%\label{sub:constructing_service_requests}

We now illustrate the interaction with RESTful services on simple GET requests\footnote{Other methods such as POST or SOAP-based services are also supported.}. 
In this case, a service request is assembled using its URL and a set of parameters. As an example, we will look at the eBay Shopping web service. 
To define the desired pre-condition and the type of post-condition of a new service wrapper, the service wrapper tool provides a form (not shown here). For the current example, we assume that the user has defined a pre-condition \emph{search\_key}.
We are invoking the service to retrieve a list of items corresponding to the search keyword ``USB'':

@@

%\subsection{Interpreting Service Responses} % (fold)
%\label{sub:interpreting_service_responses}

@@

\begin{figure}
  \begin{center}     
    \includegraphics[height=\linewidth, angle=90]{images/ServiceWrapperToolGVSWithTransformationRules.png}
    \caption{Rule-based transformation of service response}
    \label{fig:response_service_execution}
  \end{center}
\end{figure}

@@

%\subsection{Generating the Service Wrapper} % (fold)
%\label{sub:generating_a_resource_adapter}
